\propertitle

### 2019-07-11 maxNt_v5.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-07-11T13:29:31+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

Now consider the related question: What is the activity $\yA_{t}$ of the
full network at some specific time bin $t$? If we don't know the exact
sequence of activities during the recording then we don't know $\yA_{t}$;
if we know the frequency distribution $\yF$ of the activity levels, then
our probability for $\yA_{t}$ is $\yFF_{\yA_{t}}$, out of combinatorial
reasons. But if we are also uncertain about $\yF$, with
probability~\eqref{eq:density_F}, then our probability for $\yA_{t}$ by
marginalization is
\begin{equation}
  \label{eq:probability_AT}
  \pf(\yA_{t} \| \yD \yI) =
  \int \yFF_{\yA_{t}}\;   \pf(\yF \| \yD \yI)\;\di\yF;
\end{equation}
our probability distribution for $\yA_{t}$ is thus simply the mean
$\int \yF\; \pf(\yF \| \yD \yI)\;\di\yF$.

@@

***mode of marginal can be very different from the one in full space
(minka1998)

*** diff position of mode in marginals says that full distr is extremely
skewed – not surprising since the base space is bounded.

***in-depth discussion about underlying assumptions, derivation from
probability calculus, higher-order approximations beyond maxent and
"error bars" around the distributions

***We can ask about probability of bimodality etc

\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/MC_plot1000.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/MC_samples1000.pdf}%
\caption{***}
\label{fig:comparisons_marginals}
\end{figure}
% mctests3.nb
% mcfd_6mom_unif_afssd40st0np_cok_tr_N1000_t50_L50_T0.333333333333333_s60000_a15758.0500981316

\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/MC_plot5000.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/MC_samples5000.pdf}%
\caption{***}
\label{fig:comparisons_marginals}
\end{figure}
% mctests3.nb
% mcfd_6mom_unif_afssd32s_cok_tr_N5000_t180_L50_T0.333333333333333_s25800_a329212306.071189

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-07-11T14:53:17+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

Now consider the related question: What is the activity $\yA_{t}$ of the
full network at some specific time bin $t$? If we don't know the exact
sequence of activities during the recording then we don't know $\yA_{t}$;
if we know the frequency distribution $\yF$ of the activity levels, then
our probability for $\yA_{t}$ is $\yFF_{\yA_{t}}$, out of combinatorial
reasons. But if we are also uncertain about $\yF$, with
probability~\eqref{eq:density_F}, then our probability for $\yA_{t}$ by
marginalization is
\begin{equation}
  \label{eq:probability_AT}
  \pf(\yA_{t} \| \yD \yI) =
  \int \yFF_{\yA_{t}}\;   \pf(\yF \| \yD \yI)\;\di\yF;
\end{equation}
our probability distribution for $\yA_{t}$ is thus simply the mean
$\int \yF \pf(\yF \| \yD \yI)\,\di\yF$.

@@

\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/MC_plot1000.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/MC_marginal1000.pdf}%
\caption{***}
\label{fig:MC1000}
\end{figure}
% mctests3.nb
% mcfd_6mom_unif_afssd40st0np_cok_tr_N1000_t50_L50_T0.333333333333333_s60000_a15758.0500981316
\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/MC_plot5000.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/MC_marginal5000.pdf}%
\caption{***}
\label{fig:MC5000}
\end{figure}
% mctests3.nb
% mcfd_6mom_unif_afssd32s_cok_tr_N5000_t180_L50_T0.333333333333333_s25800_a329212306.071189
The properties of the belief density~\eqref{eq:density_proportional} are
shown in \fig~\ref{fig:MC1000} for $N=1\,000$ and in \fig~\ref{fig:MC5000}
for $N=5\,000$, considering the first six factorial moments as our data. It
turns out that that six moments lead to practically the same result as
specifying the full frequency distribution for the sample; they are therefore
informationally sufficient.

The top plots in the figures show the mean
$\int \yF \pf(\yF \| \yD \yI)\,\di\yF$
(\textcolor{myblue}{\textbf{------}}), which is also our belief about the
activity at any single time bin, \eqn~\eqref{eq:probability_AT}, is clearly
different from the maximum-entropy mode. The latter is therefore not a good
approximation for the full density~\eqref{eq:density_proportional}, which
is quite broad, as can be seen from the ten samples
(\textcolor{mygreen}{------}) drawn from it. The mean and the
maximum-entropy mode are nevertheless qualitatively similar. In fact, for
$N=1\,000$ the second peak of the mean is even higher than the
corresponding maximum-entropy one. The samples also show that generally two
main frequency peaks of activity are expected, especially for $N=5\,000$.
